Beyond Adaptive Web Design

### 2014-02-19 paper/paper.tex
style: fix quotation

The basic approach how to provide an optimal viewing experience is to use Responsive web design which comes with fluid grids, flexible images and CSS3 media queries~\cite{responsive}. While creating flexible layouts is important, there’s a whole lot more that goes into truly exceptional adaptive web experiences. The principles of Adaptive Design are: ubiquity, flexibility, performance, enhancement and future-friendliness~\cite{adaptivesxsw}.

The power of the web is its ubiquity. No one knows what the landscape is going to look like in a couple years, but there’s a good chance the new devices in a few years from now will have access to the web. Because of this, we need to preserve and embrace the web’s ubiquity. This requires us to deliver full web experiences regardless of how and where people access the web. It's important to continue creating flexible interfaces that can adapt to any screen size. Performance often takes a back seat to everything else. Progressive enhancement, feature detection and many other techniques allow us to build up a core experience that allow us to support more devices while still optimizing for the the best of the best. The key aspect of Future Friendly thinking is to acknowledge and embrace unpredictability. Nobody knows where things are going but the one thing we can count on is the evolution.

Adaptive web design is essentially progressive enhancement at its core, but it’s being applied to a much larger, more diverse landscape than when the term progressive enhancement was first coined. We now have Web-enabled smartphones, tablets, e-readers, netbooks, watches, TVs, phablets, notebooks, game consoles, cars and more. We also have many types of internet connections with different qualities.

Responsive design is one technique in an adaptive web design strategy. Creating flexible layouts is extremely important, but it’s just one piece of the puzzle. It’s also important to consider a whole host of other factors as well: ergonomics, touch capability and other input methods, internet connection, geolocation and many other features that can be detected.

We consider “adaptive web design” as a synonym with creating a single Web experience that modifies based on the capabilities of the device and browser. Website can access superpowers in devices.

@@

We also have wearable computers. The current Google Glass interface is limited to a floating rectangle above head. We don’t have full range of motion and, as a result, no spatial cues or depth in the interface.

@@

The optimal touch target size is 7mm, based on the average size of human finger tips and pads. CSS2.1 defines a pixel as 1/96 of an inch. So 7mm should be 30pixels~\cite{designingfortouch}. However, things aren’t so easy because of dynamic viewports. It means that input elemtents in website have to be usually bigger.

@@

We use the Mobile First principe so we make a default elemet static and pull in a static image. This approach saves a lot of web traffic and becasue of limited mobile internet plans also user's money. We can then detect when it’s appropriate to download the embedded map or to launch the native mobile application.

>>>>

The basic approach how to provide an optimal viewing experience is to use Responsive web design which comes with fluid grids, flexible images and CSS3 media queries~\cite{responsive}. While creating flexible layouts is important, there's a lot more that goes into truly exceptional adaptive web experiences. The principles of Adaptive Design are: ubiquity, flexibility, performance, enhancement and future-friendliness~\cite{adaptivesxsw}.

The power of the web is its ubiquity. No one knows what the landscape is going to look like in a couple years, but there's a good chance the new devices in a few years from now will have access to the web. Because of this, we need to preserve and embrace the web's ubiquity. This requires us to deliver full web experiences regardless of how and where people access the web. It's important to continue creating flexible interfaces that can adapt to any screen size. Performance often takes a back seat to everything else. Progressive enhancement, feature detection and many other techniques allow us to build up a core experience that allow us to support more devices while still optimizing for the the best of the best. The key aspect of Future Friendly thinking is to acknowledge and embrace unpredictability. Nobody knows where things are going but the one thing we can count on is the evolution.

Adaptive web design is essentially progressive enhancement at its core, but it's being applied to a much larger, more diverse landscape than when the term progressive enhancement was first coined. We now have Web-enabled smartphones, tablets, e-readers, netbooks, watches, TVs, phablets, notebooks, game consoles, cars and more. We also have many types of internet connections with different qualities.

Responsive design is one technique in an adaptive web design strategy. Creating flexible layouts is extremely important, but it's just one piece of the puzzle. It's also important to consider a whole host of other factors as well: ergonomics, touch capability and other input methods, internet connection, geolocation and many other features that can be detected.

We consider ``adaptive web design'' as a synonym with creating a single Web experience that modifies based on the capabilities of the device and browser. Website can access superpowers in devices.

@@

We also have wearable computers. The current Google Glass interface is limited to a floating rectangle above head. We don't have full range of motion and, as a result, no spatial cues or depth in the interface.

@@

The optimal touch target size is 7mm, based on the average size of human finger tips and pads. CSS2.1 defines a pixel as 1/96 of an inch. So 7mm should be 30pixels~\cite{designingfortouch}. However, things aren't so easy because of dynamic viewports. It means that input elemtents in website have to be usually bigger.

@@

We use the Mobile First principe so we make a default elemet static and pull in a static image. This approach saves a lot of web traffic and becasue of limited mobile internet plans also user's money. We can then detect when it's appropriate to download the embedded map or to launch the native mobile application.
